Neural Networks for Neural Tumors\\ \vspace{-0.6em} {\footnotesize Final Project for \textit{ECS 171 - Machine Learning} at UC Davis, with Professor Setareh Rafatirad}

### 2025-06-05 latex/draft.tex
cleaned up tables, removed weighted and macro averages, and support column
Update draft.tex

\begin{table}[h!]
\centering
\caption{CNN Metrics}
\begin{tabular}{lcccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\
\midrule
glioma     & 0.98 & 0.93 & 0.95 & 109 \\
meningioma & 0.93 & 0.97 & 0.95 & 105 \\
no tumor   & 0.97 & 0.98 & 0.98 & 60  \\
pituitary  & 0.99 & 0.99 & 0.99 & 118 \\
\midrule
\textbf{Accuracy}    &      &      & 0.97 & 392 \\
\textbf{Macro avg}   & 0.97 & 0.97 & 0.97 & 392 \\
\textbf{Weighted avg}& 0.97 & 0.97 & 0.97 & 392 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{SVM Metrics}
\begin{tabular}{lcccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\
\midrule
glioma     & 0.98 & 0.91 & 0.94 & 109 \\
meningioma & 0.89 & 0.97 & 0.93 & 105 \\
no tumor   & 0.98 & 0.97 & 0.97 & 60  \\
pituitary  & 0.98 & 0.98 & 0.98 & 118 \\
\midrule
\textbf{Accuracy}    &      &      & 0.96 & 392 \\
\textbf{Macro avg}   & 0.96 & 0.96 & 0.96 & 392 \\
\textbf{Weighted avg}& 0.96 & 0.96 & 0.96 & 392 \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{RF Metrics}
\begin{tabular}{lcccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} & \textbf{Support} \\
\midrule
glioma     & 0.98 & 0.89 & 0.93 & 109 \\
meningioma & 0.87 & 0.98 & 0.92 & 105 \\
no tumor   & 1.00 & 0.93 & 0.97 & 60  \\
pituitary  & 0.97 & 0.98 & 0.98 & 118 \\
\midrule
\textbf{Accuracy}    &      &      & 0.95 & 392 \\
\textbf{Macro avg}   & 0.96 & 0.95 & 0.95 & 392 \\
\textbf{Weighted avg}& 0.95 & 0.95 & 0.95 & 392 \\
\bottomrule
\end{tabular}
\end{table}

@@

Jonathan: Jonathan took charge of literature review and researched techniques that can be implemented to the model. In the next few weeks, Jonathan will be focusing on writing the proposed methodology for the final report.

>>>>

\begin{table}[h!]
\centering
\caption{CNN Metrics}
\begin{tabular}{lccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} \\
\midrule
glioma     & 0.98 & 0.93 & 0.95 \\
meningioma & 0.93 & 0.97 & 0.95 \\
no tumor   & 0.97 & 0.98 & 0.98 \\
pituitary  & 0.99 & 0.99 & 0.99 \\
\midrule
\textbf{Accuracy} \textbf{0.97} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}[h!]
\centering
\caption{SVM Metrics}
\begin{tabular}{lccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} \\
\midrule
glioma     & 0.98 & 0.91 & 0.94 \\
meningioma & 0.89 & 0.97 & 0.93 \\
no tumor   & 0.98 & 0.97 & 0.97 \\
pituitary  & 0.98 & 0.98 & 0.98 \\
\midrule
\textbf{Accuracy} \textbf{0.96} \\
\bottomrule
\end{tabular}
\end{table}

\begin{table}
\centering
\caption{RF Metrics}
\begin{tabular}{lccc}
\toprule
\textbf{Class} & \textbf{Precision} & \textbf{Recall} & \textbf{F1-score} \\
\midrule
glioma     & 0.98 & 0.89 & 0.93 \\
meningioma & 0.87 & 0.98 & 0.92 \\
no tumor   & 1.00 & 0.93 & 0.97 \\
pituitary  & 0.97 & 0.98 & 0.98 \\
\midrule
\textbf{Accuracy} \textbf{0.95} \\
\bottomrule
\end{tabular}
\end{table}

@@

Jonathan: Jonathan took charge of literature review and researched techniques that can be implemented to the model. Jonathan was also responsible for writing the evaluation section that analyzed the performances of the models by talking about the evaluation metrics such as F1 scores, precision, and recall across the different classes.
